Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
typo

Though Scala doesn't have virtual classes, its abstract types enables
it to emulate some (but not all) of the benefits of virtual classes as
presented in the Tribe calculus. On the other hand, Tribe doesn't have
virtual types. In a follow-up paper~\cite{tribalo}, an improved
variant of Tribe with simpler types, cross-family inheritance and
generics is presented and a formalisation of ownership types built
upon it.

>>>>

Though Scala doesn't have virtual classes, its abstract types enable
it to emulate some (but not all) of the benefits of virtual classes as
presented in the Tribe calculus. On the other hand, Tribe doesn't have
virtual types. In a follow-up paper~\cite{tribalo}, an improved
variant of Tribe with simpler types, cross-family inheritance and
generics is presented and a formalisation of ownership types built
upon it.
